true

### 2020-04-27 analysis/robinson2020.Rmd
getting travis working

@@

```{r gc2, echo = FALSE, message = FALSE, results='hide'}
gc()
gc()
```

@@

```{r gc, echo = FALSE, message = FALSE, results='hide'}
gc()
gc()
```

>>>>

```{r gc3, echo = FALSE, message = FALSE, results='hide'}
# This chunk is here to deal with memory limits of Travis CI
rm(list = ls())
gc()
gc()
```

@@

@@

```{r gc, echo = FALSE, message = FALSE, results='hide'}
# This chunk is here to deal with memory limits of Travis CI
gc()
gc()
```
